%% Content from http://zhenti.kaoyan.eol.cn/
%% Format by PythonShell
%% 2014-01-08

\qquad Research on animal intelligence always makes me wonder just how smart humans are. \underline{\quad 1\quad}   the fruit-fly experiments described by Carl Zimmer in the \emph{Science Times}. Fruit flies who were taught to be smarter than the average fruit fly \underline{\quad 2\quad}   to live shorter lives. This suggests that \underline{\quad 3\quad}   bulbs burn longer, that there is a(n) \underline{\quad 4\quad}     in not being too bright.

\qquad Intelligence, it \underline{\quad 5\quad}, is a high-priced option. It takes more upkeep, burns more fuel and is slow \underline{\quad 6\quad}    the starting line because it depends on learning-a(n) \underline{\quad 7\quad} process - instead of instinct. Plenty of other species are able to learn, and one of the things they've apparently learned is when to \underline{\quad 8\quad}.

\qquad Is there an adaptive value to \underline{\quad 9\quad}    intelligence? That's the question behind this new research. Instead of casting a wistful glance \underline{\quad 10\quad}    at all the species we've left in the dust I.Q.-wise, it implicitly asks what the real \underline{\quad 11\quad}    of our own intelligence might be. This is \underline{\quad 12\quad}   the mind of every animal I've ever met.

\qquad Research on animal intelligence also makes me wonder what experiments animals would \underline{\quad 13\quad}   on humans if they had the chance. Every cat with an owner, \underline{\quad 14\quad}   , is running a small-scale study in operant conditioning. we believe that \underline{\quad 15\quad}  animals ran the labs, they would test us to \underline{\quad 16\quad}   the limits of our patience, our faithfulness, our memory for locations. They would try to decide what intelligence in humans is really \underline{\quad 17\quad}, not merely how much of it there is.   \underline{\quad 18\quad}, they would hope to study a(n) \underline{\quad 19\quad}   question: Are humans actually aware of the world they live in? \underline{\quad 20\quad}   the results are inconclusive.

\vspace{6pt}

01. \choice{ Suppose            }{ Consider         }{  Observe                }{ Imagine}
02. \choice{ tended               }{ feared             }{  happened              }{ threatened}
03. \choice{ thinner              }{ stabler              }{  lighter                  }{ dimmer}
04. \choice{ tendency           }{ advantage        }{  inclination             }{ priority}
05. \choice{ insists on          }{ sums up          }{  turns out               }{ puts forward}
06. \choice{ off                   }{ behind             }{  over                     }{ along}
07. \choice{ incredible          }{ spontaneous   }{ inevitable                 }{ gradual}
08. \choice{ fight                 }{ doubt             }{  stop                       }{ think}
09. \choice{ invisible            }{ limited           }{  indefinite                 }{ different}
10. \choice{ upward           }{ forward         }{  afterward               }{ backward}
11. \choice{ features           }{ influences      }{  results                   }{ costs}
12. \choice{ outside            }{ on                 }{  by                         }{ across}
13. \choice{ deliver             }{ carry             }{    perform             }{ apply}
14. \choice{ by chance        }{ in contrast     }{  as usual                }{ for instance}
15. \choice{ if                    }{ unless            }{  as                        }{ lest}
16. \choice{ moderate         }{ overcome      }{  determine             }{ reach}
17. \choice{ at                    }{ for               }{  after                     }{ with}
18. \choice{ Above all         }{ After all         }{  However              }{ Otherwise}
19. \choice{ fundamental     }{ comprehensive    }{  equivalent        }{ hostile}
20. \choice{ By accident      }{ In time                  }{  So far                 }{ Better still}