Dear editor,

As a faithful reader, I always appreciate your active reporting of the social problems. I hope you would also pay attention to the abuse of plastic bags unchanged in some regions.

Environmentally speaking, the usage of plastic bags should be reduced. To achieve it, the government should further strengthen the control of the production and circulations. Shops can offer small gifts or discounts to customers who boycott plastic bags. Designers can beautify cloth bags to attract users from plastic bags.

Since my own voice is too weak to be heard, I hope you could call on the public to fullfil the restrictions on plastic bags.

\begin{flushright}Yours sincerely,

Li Ming\end{flushright}

An enormous net, which symbolizes the Internet, has connected together everyone---young and old, men and women. People from every corner of the world are keeping in touch with each other just by pressing the keyboard or the mouse. With its convenience and efficiency, the Internet is narrowing the distance between people in terms of spaces.

However the picture also shows: while people enjoy surfing online, walls of barrier emerge unnoticed and restrict each one of people to a narrow space. As the time spent on the Internet is on the rise, face to face communication has experienced a rapid drop. The reduction of contact in reality may result in feelings of loneliness and isolation, which will destroy interpersonal relationships. It can be illustrated by the exanple of a young couple. They lived happily until the third year of their marriage when both of them became addicted to the Internet. They, squandering time on surfing the Internet each with a computer in different rooms, gradually lost the desire to talk with each other and eventually divorced.

This tragic story reminds us that we shouldn't over relyon the Internet to communicate. After all, the virtual net world cannot be a substitute for te real world. Therefore, we must make use of the Internet judiciously and interact with others actively in social activities.