\qquad The idea that some groups of people may be more intelligent than others is one of those hypotheses that dare not speak its name. But Gregory Cochran is \underline{\quad 1\quad}  to say it anyway. He is that \underline{\quad 2\quad}  bird, a scientist who works independently \underline{\quad 3\quad}  any institution. He helped popularize the idea that some diseases not \underline{\quad 4\quad}  thought to have a bacterial cause were actually infections, which aroused much controversy when it was first suggested.

\qquad \underline{\quad 5\quad} he, however, might tremble at the \underline{\quad 6\quad}  of what he is about to do. Together with another two scientists, he is publishing a paper which not only \underline{\quad 7\quad}  that one group of humanity is more intelligent than the others, but explains the process that has brought this about. The group in \underline{\quad 8\quad} are a particular people originated from central Europe. The process is natural selection.

\qquad This group generally do well in IQ test, \underline{\quad 9\quad} 12-15 points above the \underline{\quad 10\quad}  value of 100, and have contributed \underline{\quad 11\quad}  to the intellectual and cultural life of the West, as the \underline{\quad 12\quad}  of their elites, including several world-renowned scientists, \underline{\quad 13\quad} they also suffer more often than most people from a number of nasty genetic diseases, such as breast cancer. These facts, \underline{\quad 14\quad} ave previously been thought unrelated. The former has been \underline{\quad 15\quad}  social effects, such as a strong tradition of \underline{\quad 16\quad} ucation. The latter was seen as a (an) \underline{\quad 17\quad} genetic isolation. Dr. Cochran suggests that the intelligence and diseases are intimately \underline{\quad 18\quad} is argument is that the unusual history of these people has \underline{\quad 19\quad} em to unique evolutionary pressures that have resulted in this \underline{\quad 20\quad} ate of affairs.

01. \choice{ selected}{ prepared}{ obliged}{ pleased}
02. \choice{ unique}{ particular}{ special}{ rare}
03. \choice{ of}{ with}{ in}{ against}
04. \choice{ subsequently}{ presently}{ previously}{ lately}
05. \choice{ Only}{ So}{ Even}{ Hence}
06. \choice{ thought}{ sight}{ cost}{ risk}
07. \choice{ advises}{ suggests}{ protests}{ objects}
08. \choice{ progress}{ fact}{ need}{ question}
09. \choice{ attaining}{ scoring}{ reaching}{ calculating}
10. \choice{ normal}{ common}{ mean}{ total}
11. \choice{ unconsciously}{ disproportionately}{ indefinitely}{ unaccountably}
12. \choice{ missions}{ fortunes}{ interests}{ careers}
13. \choice{ affirm}{ witness}{ observe}{ approve}
14. \choice{ moreover}{ therefore}{ however}{ meanwhile}
15. \choice{ given up}{ got over}{ carried on}{ put down}
16. \choice{ assessing}{ supervising}{ administering}{ valuing}
17. \choice{ development}{ origin}{ consequence}{ instrument}
18. \choice{ linked}{ integrated}{ woven}{ combined}
19. \choice{ limited}{ subjected}{ converted}{ directed}
20. \choice{ paradoxical}{ incompatible}{ inevitable}{ continuous}