Dear Bob,

As I was unpacking the luggage after my return from Canada, I came across the music CD borrowed from you there last week. It dawned on me that I had forgotten to return the CD. I feel terribly sorry. I was so busy perparing for my leave that it must have slipped my mind.

To make up for my carelessness, I have mailed the CD through EMS, along with a book written by your favorite Chinese writer, Lu Xun. They will reach you in about one week. Again, I would like to apologize for any inconvenience it may have caused you.

\begin{flushright}Yours sincerely,

Li Ming\end{flushright}

Do you regard it as a tale from \emph{The Thousand and One Nights} if I say that two single-legged men stride forward without crutches they have to rely on? The above drawing depicts this touching miracle. With the support of each other, they abandon their walking sticks and, just as the caption at the bottom states, are going to travel extensively from north to south together with their combined legs.

The picture shows: even disabled people can make up a capable team. It can be vividly illustrated by the beautiful dance Kwan-yin of 1,000 Hands performed by 20 disabled girls during the CCTV Spring Festival Gala. With the perfect cooperation, these deaf mute girls change disadvantages into advantages, the impossible into possible.

Cooperation is an essential element of success. Without cooperation, a person cannot accomplish much in the increasing inter-dependent society we now live in. It is cooperation based on the complementary advantages that contributes to the ultimate success. Also, the spirit of cooperation should be embraced by every nation in the world. China, for instance, has been actively participating in the cooperation with other countries in various fields in order to achieve the goal of win-win and common development.