Dear Sir,

On behalf of the students' union, I'm writing to invite you to judge our English speech competition from April 28 to 39 at the auditorium. 35 competitors will compete for awards in this contest. These participants are required to first give a prepared speech on \emph{how to live productively} and then answer 5 randomly-picked questions. You are expected to score and comment on their performance.

You, an academic elite and native English speaker, are a godlike figure in English learners' eyes, so your presence in the competition as a judge is very significant to the participating students. We will feel greatly hornored to have you there and appreciate it if you could reply to our invitation at your earliest convenience.

\begin{flushright}Yours sincerely,

Li Ming\end{flushright}

In the above picture, a flock of graduates are stopped by a four-direction fork. The directions symbolize four life choices after graduation, namely.seeking employment, taking the postgraduate entrance exam, going abroad for further study and starting a buiness.

Understandably, university graudates, now without the glory of intellectual elites, are facing an uncertain future and hesitant to make a choice out of a variety of possibilities. However, this picture does not imply so much the dilemma in which graduates are caught as the encouragingly unprecedented life possibilities. It seems true that today's university graduates are under greater employment pressure and in face of a steeper social ladder. This uncomfortable situation can not obscure the fact --- compared with their parents and grandparents, current graduates are given considerable freedom to dream and fulfill their dreams. They can, with little social restraint, expand knowledge, broaden personal experience and choose careers they are interested in.

The life of today's university graduates is full of promise. However, most graduates don't realize and accept it. Some repeatedly complain about their limits, mostly financial or professional ones. These people ignore their potential to change thmeselves and their life. Actually, all desired life goals can be achieved through diligence, persistence and willingness to learn continuously. Therefore, university graduates are encouraged to follow their interest and advance bravely along their chosen life paths.