\begin{center}\textbf{Recruitment Announcement}\end{center}

Do you want to be a part of a high-level international conference and have close contact with world famous scholars? Here comes your opportunityL becoming a volunteer for the 2010 international conference on globalization.

The conference will open in our university on Feb. 28. To ensure its success, 50 volunteers will be recruited. If you possess basic English speaking ability, good communication skills and tremendous working enthusiasm, you will be the ideal candidate we are looking for.

What a great chance it is to display your talents! To seize such a marvelous opportunity, you just need to send your resume to our office in room 302 of the Teaching Building 5 before Feb. 12. For more details, please contact 12345678.

\begin{flushright}Postgraduates' Association\end{flushright}

The picture presents a steaming "cultural hotpot", which contains a variety of ingredients of culture, both ancient and modern, Chinese and foreign. These cultural ingredients, such as Swan Lake, Confucianism and Einstein, are tremendously delicious and nutritious when combined together. What a great cultural feast! This drawing implies a prevailing trend -- the integration of global cultures.

The blend of worldwide cultures could be much "tasty". Just as meat or vegetables taste especially delicious when boiled together in a hotpot, cultures become extraordinarily attractive when integrating. The integration provides an abundance of cultures for people to experience, not only native ones but also alien ones.

The culture blending could also bring adequate spiritual "nourishment" for human beings. Both Chinese and foreigners benefit a lot from absorbing different but complementary cultures. For instance, Westerners could enrich their artistic understanding by means of learining Kong Fu or appreciating Peking Opera while Chinese could also improve their level of artistic appreciation through watching western classical ballets like Swan Lake. More illustratively, Chinese traditional philosophy, Confucianism, has been introduced, accepted and applied into practical use in the western world to improve modern management; the Enlightenment from the West has helped Chinese to break the bonds of feudalism and supplied the thought basis for China's social changes in the end of 20th Century.