Dear Sir or Madam,

As a freshman in our university. I do appreciate the valuable service provided in the library where I spend most of my spare time absorbing knowledge. To help improve the service, I would like to put forward some practical suggestions.

Firstly, there is an urgent need for more powerful computers which can greatly facilitate our information search and learning process. Secondly, it would be considerate if the library could purchase more recently published books, since the outdated materials are of little value to students' study and research. Lastly, as we'd like to borrow books on Saturdays as well, I wish the opening time could be adjusted.

I will be more than happy to see improvements in these regards.

\begin{flushright}Yours sincerely,

Li Ming\end{flushright}

A football match has reached its climax before a critical penalty kick. The football is waiting for a powerful and accurate kick from the attacker while the goalkeeper, watching it closely, has prepared himself to defend the goal. Suddenly, confidence-destroying images emerge. In the imagination of the attacker, the goalkeeper grows into a giant and shooting in seems unachievable. Meanwhile, the defender thinks poorly of himself and despairs of keeping good guard.

Seemingly, the message of this picture is that people will underestimate their abilities and magnify difficulties when confronted with challenges. Actually, this picture is aimed to warn us that people with tremendous potential usually bury their success chances under stones of self-doubt, which shatters their willpower and hope. To awake one's dormant spirit and seek a huge success, unshakable self-confidence is indispensable.

Numerous examples can demonstrate the power of self-confidence. For instance, despite the fierce competition, students believing in themselves often excel in the postgraduate entrance exam. Another example is about Deng Yaping, an internationally famous athlete, whose short figure doesn't stop her from becoming a legend in the table tennis field. Her perserverance and strong will have enabled her to win not only 18 major world champions but also respect from all over the world.