My dear friend,

I can't wait to recommend you \emph{The Pursuit of Happyness}, a film which I watched last night and whose plot still haunts me.

The film explores the meaning of love, optimism, persistence, and, certainly, happiness. It is in spired by the true story of Chris Gardner, a salesman struggling to build a future for himself and his 5-year-old son. Besides its touching and inspiring story, this film is recommendable for its great reputation. It has created a box office miracle and won numerous international prizes. Another appealing feature of this film is a coincidence: it stars Will Smith, an American actor, and his real life son.

I am sure you will love this film. Hope to discuss it with you later.

\begin{flushright}Yours,

Li Ming\end{flushright}

Two tourists are sitting on the edge of a boat. They recklessly discard rubbish while enjoying their fantastic trip. Unbelievably, the boatman continues to quietly pole his boat pretending that he doesn't see their improper behaviors. Downstream floats cans, bottles, snack bags and foot leftovers---a variety of rubbish. The scattered garbage has spoiled the previously scenic lake.

This picture warns us that the serious environmental problem is facing scenic spots around China. Li Jiang, Qin Emperor Mausoleum, Beijing Historic Districts are threatened by piles of smelly rubbish. It is a man made problem. Some selfish people, as picture indicates, throw their waste at their will while others, even some officers in scenic spots, turn a blind eye on it. It is not uncommon to meet tourists who refuse to take their rubbish few steps further to the dustbin. However, it is rare to see people who stand out to stop such misconducts.

Since human activities are to blame for environmental degradation in tourism spots, human beings should assume their responsibility to reverse the worrying trend. Tourists should be aware of the necessity of protecting environment and volunteer to act as environment protectors. Offices in attraction resorts should offer effective supervision and impose harsh punishment on environment destroyers. Hopefully, tourist resorts could gradually regain attraction through joint efforts.