My dear friends,

I, on behalf of the students' union, wnat to extend my warm welcome to you. I am happy that you have chosen to receive college education in our university in China.

To make your life here easier, I'd like to offer several suggestions. You should first, to overcome language barriers, study and diligently practice Chinese--the language necessary for you to follow lessons and exchange ideas with your Chinese professors. Besides, you'd better strive to relive the culture shock. It is advisable to learn Chinese culture through making Chinese friends and traveling around or from books, films and museums.

I hope my suggestions would be helpful and wish all of you a fulfilling college life here.

\begin{flushright}Yours sincerely,

Li Ming\end{flushright}

A bottle had fallen down, with half of its water pouring out. To the scene, two men responded differently. One man, feeling extremely sad, his hand covering his face, sighed "All has gone!" The other seemed much more optimistic. He ran happily to raise up the bottle and said with great gratitude "There is still some water left."

Why did the two people have such distinct reaction? It is because they judged the situation from opposite perspectives. After the bottle fell, the pessimistic observer focused on the losses thereby thinking negatively, while the other observer noticed the remaining liquid and then had a positive opinion. Actually, the fallen bottle is a symbol of unfortunate circumstances in life and the two kinds of responses reflect two different attitudes towards misfortunes.

Misfortunes mean obvious losses; however they still bring latent opportunities to people with optimistic mind. From the perspective of optimists, firing, a career disaster, will be a reminder of the necessity for an urgent improvement in their personality or expertise. Sensing the signal for change, those optimists will strive to achieve personal growth, the growth which provides a guarantee for healthier career development in future. Misfortunes are blessings in disguise and optimism can unlock the cover. Therefore, in the face of misfortunes people should adopt an optimistic attitude.