%% Content from http://zhenti.kaoyan.eol.cn/
%% Format by PythonShell
%% 2014-01-07

\qquad The homeless make up a growing percentage of America's population. \underline{\quad 1\quad}, homelessness has reached such proportions that local government can't possibly \underline{\quad 2\quad}. To help homeless people \underline{\quad 3\quad} independence, the federal government must support job training programs, \underline{\quad 4\quad} the minimum wage, and fund more low-cost housing.

\qquad \underline{\quad 5\quad} everyone agrees on the number of Americans who are homeless. Estimates \underline{\quad 6\quad} anywhere from 600,000 to 3 million. \underline{\quad 7\quad} the figure may vary, analysts do agree on another matter: that the number of the homeless is \underline{\quad 8\quad}. One of the federal government's studies \underline{\quad 9\quad} that the number of the homeless will reach nearly 19 million by the end of this decade.

\qquad Finding ways to \underline{\quad 10\quad} this growing homeless population has become increasingly difficult. \underline{\quad 11\quad} when homeless individuals manage to find a \underline{\quad 12\quad} that will give them three meals a day and a place to sleep at night, a good number still spend the bulk of each day \underline{\quad 13\quad} the street. Part of the problem is that many homeless adults are addicted to alcohol or drugs. And a significant number of the homeless have serious mental disorders. Many others, \underline{\quad 14\quad} not addicted or mentally ill, simply lack the everyday \underline{\quad 15\quad} skills need to turn their lives \underline{\quad 16\quad}. \emph{Boston Globe} reporter Chris Reidy notes that the situation will improve only when there are \underline{\quad 17\quad} programs that address the many needs of the homeless. \underline{\quad 18\quad} Edward Blotkowski, director of community service at Bentley College in Massachusetts, \underline{\quad 19\quad} it, ``There has to be \underline{\quad 20\quad} of programs. What we need is a package deal.''

\vspace{6pt}

01. \choice{ Indeed }{ Likewise }{ Therefore }{ Furthermore}
02. \choice{ stand }{ cope }{ approve }{ retain}
03. \choice{ in }{ for }{ with }{ toward}
04. \choice{ raise }{ add }{ take }{ keep}
05. \choice{ Generally }{ Almost }{ Hardly }{ Not}
06. \choice{ cover }{ change }{ range }{ differ}
07. \choice{ Now that }{ Although }{ Provided }{ Except that}
08. \choice{ inflating }{ expanding }{ increasing }{ extending}
09. \choice{ predicts }{ displays }{ proves }{ discovers}
10. \choice{ assist }{ track }{ sustain }{ dismiss}
11. \choice{ Hence }{ But }{ Even }{ Only}
12. \choice{ lodging }{ shelter }{ dwelling }{ house}
13. \choice{ searching }{ strolling }{ crowding }{ wandering}
14. \choice{ when }{ once }{ while }{ whereas}
15. \choice{ life }{ existence }{ survival }{ maintenance}
16. \choice{ around }{ over }{ on }{ up}
17. \choice{ complex }{ comprehensive }{ complementary }{ compensating}
18. \choice{ So }{ Since }{ As }{ Thus}
19. \choice{ puts }{ interprets }{ assumes }{ makes}
20. \choice{ supervision }{ manipulation }{ regulation }{ coordination}