Dear Sir or Madam,

I am writing to ask whether you can recommend a child as the recipient of my financial assistance.

To be specific, I hope to help a dropout girl from a remote and poor area in West China. I will take care of her tuition until she finishes college and additionally provide her with 200- yuan living expenses each month.

I hope you could help me to realize my wish to contribute to educational development in remote areas. Please contact me when you find a proper candidate. It would be very helpful if you could send me her photo and personal information. I appreciate your valuable attention and hope to hear from you soon.

\begin{flushright}Yours sincerely,

Li Ming\end{flushright}

As is shown in the two photos, one man has written "Beckham" on his face and the other is squandering RMB 300 on Beckham's hairstyle. How mad their behaviors are!

The photos have revealed a current social phenomenon that some young people are crazily following superstars. These over-ardent admirers devote almost all the time and energy to the pursuit of stars. Rationally speaking, their admiration is superficial and short-sighted because their attention is mainly concentrated on the physical appearance rather than the soul force of the stars. Few of the youngsters can realize the achievements the superstars have attained are from their diligence and perseverance.

In my opinion, though the appreciation of idols itself gives little cause for criticism, the young should admire and immitate their idols in a proper way. It is not worthwhile for the young people to hurt themselves or spend extravagantly for the purpose of imitating idols. Idol worship is not necessarily bad and real heroes can inspire the young generation to bravely pursue better life and brighter future. To have a good result, the society should encourage the young people to focus their attention on good qualities which help the stars succeed and the young people themselves should learn hwo to work hard to earn their own honor like their idols.