People are, on the whole, poor at considering background
information when making individual decisions. At first glance this
might seem like a strength that \underline{\quad 1\quad} the
ability to make judgments which are unbiased by
\underline{\quad 2\quad} factors. But Dr Simonton speculated that
an inability to consider the big \underline{\quad 3\quad} was
leading decision-makers to be biased by the daily samples of
information they were working with. \underline{\quad 4\quad}, he
theorized that a judge \underline{\quad 5\quad} of appearing too
soft \underline{\quad 6\quad}crime might be more likely to send
someone to prison \underline{\quad 7\quad} he had already sentenced
five or six other defendants only to forced community service on
that day.

To \underline{\quad 8\quad} this idea, they turned their attention
to the university-admissions process. In theory, the \underline{\quad 9\quad} of an
applicant should not depend on the few others \underline{\quad 10\quad} randomly for interview during the same day, but Dr Simonton suspected the truth was \underline{\quad 11\quad}.

He studied the results of 9,323 MBA interviews \underline{\quad 12\quad} by 31 admissions officers. The interviewers had \underline{\quad 13\quad} applicants on a scale of one to five. This scale \underline{\quad 14\quad} numerous factors into consideration. The scores were \underline{\quad 15\quad} used in conjunction with an applicant’s score on the GMAT, a standardized exam which is \underline{\quad 16\quad} out of 800 points, to make a decision on whether to accept him or her.

Dr Simonton found if the score of the previous candidate in a daily series of interviewees was 0.75 points or more higher than that of the one \underline{\quad 17\quad} that, then the score for the next applicant would \underline{\quad 18\quad} by an average of 0.075 points. This might sound small, but to \underline{\quad 19\quad} the effects of such a decrease a candidate would need 30 more GMAT points than would otherwise have been \underline{\quad 20\quad}.

\begin{tabbing}
\hspace{0cm}
\=1.  \quad\= [A] grants \quad\quad\= [B] submits \quad\quad\= [C] transmits \quad\quad\= [D] delivers\\
\>2.  \> [A] minor     \> [B] external   \> [C] crucial      \> [D] objective\\
\>3.  \> [A] issue     \> [B] vision     \> [C] picture      \> [D] moment\\
\>4.  \> [A] Above all \> [B] On average \> [C] In principle \> [D] For example\\
\>5.  \> [A] fond      \> [B] fearful    \> [C] capable      \> [D] thoughtless\\
\>6.  \> [A] in        \> [B] for        \> [C] to           \> [D] on\\
\>7.  \> [A] if        \> [B] until      \> [C] though       \> [D] unless\\
\>8.  \> [A] test      \> [B] emphasize  \> [C] share        \> [D] promote\\
\>9.  \> [A] decision  \> [B] quality    \> [C] status       \> [D] success\\
\>10. \> [A] found     \> [B] studied    \> [C] chosen       \> [D] identified\\
\>11. \> [A] otherwise \> [B] defensible \> [C] replaceable  \> [D] exceptional\\
\>12. \> [A] inspired  \> [B] expressed  \> [C] conducted    \> [D] secured\\
\>13. \> [A] assigned  \> [B] rated      \> [C] matched      \> [D] arranged\\
\>14. \> [A] put       \> [B] got        \> [C] took         \> [D] gave\\
\>15. \> [A] instead   \> [B] then       \> [C] ever         \> [D] rather\\
\>16. \> [A] selected  \> [B] passed     \> [C] marked       \> [D] introduced\\
\>17. \> [A] below     \> [B] after      \> [C] above        \> [D] before\\
\>18. \> [A] jump      \> [B] float      \> [C] fluctuate    \> [D] drop\\
\>19. \> [A] achieve   \> [B] undo       \> [C] maintain     \> [D] disregard\\
\>20. \> [A] necessary \> [B] possible   \> [C] promising    \> [D] helpful
\end{tabbing}
