Dear Mr. Wang,

Thank you very much for having offered me this promising position to work for this best-selling magazine. It never occurred to me that I would have to leave. However, today I make the hard decision to quit it.

Painfully, I have realized that I overestimated my adaptability. My personality actually can't match the requirements of this position which highly values open mindedness and creativity. What's more, the shortage of professional knowledge, both in designing and editing, has influenced my job performance more negatively than I ever expected.

I apologize for any inconvenience I might have caused and wish you could consider my request. Please let me know if there is anything I can do to make this transition easier for the company.

\begin{flushright}Yours sincerely,

Li Ming\end{flushright}

As we can see from the picture, a football match of supporting parents is going on. The eldest son is exerting all his strength to kick away his father who is crouching like a football in the middle of the playground, while the other three children are standing in different corners, guarding their own goals. It is obvious that none of them is willing to receive the old father.

This picture does reflect a thought-provoking social phenomenon. Nowadays many young people in China regard taking care of their aged parents as a burden and refuse to take the responsibility. As a result, the old are neglected and even abandoned when growing weak and helpless.

The phenomenon reflected in the picture is both immoral and illegal. It is well-known that caring the old is not only a traditional virtue cherished by Chinese but also a duty laid down in the constitution. In order,  and, at the same time, strengthen the regulations and laws. Only in these ways can we ensure a better life for the aged.